### 2023-06-21 resilience.tex
up

Recall the {\bf Flight Controller System} example, where the safe state corresponds to the aircrafts having both landed, i.e.
$\Safe = \{(q_{A,1}, q_{M,i}, q_{B,1})(\textbf{v}) \mid \textbf{v} \in \N^4, i \in \N\}$,
and $\Bad$ is the complement of $\Safe$. 
% $\Bad = \{(q_{A,0}, q_{M,0}, q_{B,0})(\textbf{v}) \mid \textbf{v} \in \N^4\}$.
%%  Then the resilience problem asks
% wheher

@@

Given a set of states $S$, with two subsets $\Bad$ and $\Safe$, it is useful to note that in a sequence of states of $S$, every prefix is always 
either in the case that the latest visited $\Bad$ state has already been followed by a 
$\Safe$ state
or in the case that it still has to. 
Thus, \emph{in context}, there is no true ``neutral'' state: either a neutral state is contextually ``$\Safe$'' because it follows a visit in a $\Safe$ state, either it is contextually ``$\Bad$'' because it follows a visit in a $\Bad$ state and has, accordingly, to reach a $\Safe$ one.
Hence we will consider in the following not only that $\Bad$ and $\Safe$ are disjoint but
% w.l.o.g.
	also
that $\Bad$ is the complement of $\Safe$,
in which case
if $\Bad$ is downward-closed then $\Safe$ is upward-closed and vice-versa.
Cases where $\Bad$ or $\Safe$ are not complements of each other, and share closure properties, i.e. are both downward-closed or both upward-closed,
have also been studied, 
see 
Appendix~\ref{case down down}
and
Appendix~\ref{case up up} for results.

>>>>

Recall the {\bf Flight Controller System} example, where the safe state corresponds to the aircrafts having both landed, i.e.
$\Safe = \{(q_{A,1}, q_{M,i}, q_{B,1})(\textbf{v}) \mid \textbf{v} \in \N^4, i \in \N\}$,
and $\Bad$ is the complement of $\Safe$. 
% $\Bad = \{(q_{A,0}, q_{M,0}, q_{B,0})(\textbf{v}) \mid \textbf{v} \in \N^4\}$.
% wheher
The system is not $7$-resilient since there is no path of length smaller than $7$ from $(q_{A,0}, q_{M,5}, q_{B,0})(\textbf{v})$ to $\Safe$, but it is $8$-resilient.

@@

% Given a set of states $S$, with two subsets $\Bad$ and $\Safe$, 
It is useful to note that in a sequence of states% of $S$
, every prefix is always 
either in the case that the latest visited $\Bad$ state has already been followed by a 
$\Safe$ state
or in the case that it still has to. 
Thus, \emph{in context}, there is no true ``neutral'' state: either a neutral state is contextually ``$\Safe$'' because it follows a visit in a $\Safe$ state, either it is contextually ``$\Bad$'' because it follows a visit in a $\Bad$ state and has, accordingly, to reach a $\Safe$ one.
Hence we will consider in the following not only that $\Bad$ and $\Safe$ are disjoint but
% w.l.o.g.
	also
that $\Bad$ is the complement of $\Safe$,
in which case
if $\Bad$ is downward-closed then $\Safe$ is upward-closed and vice-versa.
Cases where $\Bad$ or $\Safe$ are not complements of each other, and share closure properties, i.e. are both downward-closed or both upward-closed,
have also been studied, 
see 
Appendix~\ref{case down down}
and
Appendix~\ref{case up up} for results.
